---
title: "Homework 6"
author: "Allison Randy-Cofie"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(mgcv)
library(modelr)

library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

### Problem 2
Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.


```{r}
homicide_df <- 
  read_csv("homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(city_state = str_c(city, ", ", state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% 
  filter(city_state != "Dallas, TX",
         city_state != "Phoenix, AZ",
         city_state != "Kansas City, MO",
         city_state != "Tulsa, AL") %>% 
  relocate(uid, reported_date, city_state) %>% 
  mutate(
    victim_age = as.numeric(victim_age)) %>% 
 filter(victim_race %in% c("Black" , "White"))


```


For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
baltimore_summary <- 
 homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
mutate(
    resolution = as.numeric(disposition == "Closed by arrest"))

fit = baltimore_summary %>% 
  glm(resolution ~ victim_age + victim_race + victim_sex, data = ., family = binomial())

confint(fit) 

 fit %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```


Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.
```{r}

```


Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}

```

### Problem 3
Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

 Loading the Dataset
```{r}
birthweight = read_csv("./birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
  )
str(birthweight)
#View(birthweight)
```
The are no missing values in this dataset.


Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.


I'll propose a model for this problem using backward stepwise selection. 
```{r}
model_init <- lm(bwt ~., data = birthweight)
step(model_init, direction = "backward") #type of selection
```
This model selection approach starts with all predictors in the model then removes the the least significant predictor. The process is repeated until all non-significant predictors have been removed.

The final model includes the following predictors:

* baby sex
* baby head circumference
* baby length
* mother’s weight at delivery
* family monthly income
* gestational age
* mother’s height
* mother’s race
* number of lives births prior to this pregnancy
* mother’s pre-pregnancy weight
* average number of cigarettes smoked per day during pregnancy

```{r}
#final model
model_back = lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight)
```


#### Plot of Model Residuals vs. Fitted Values.

```{r}
birthweight %>%
  add_residuals(model_back) %>%
  add_predictions(model_back) %>%
  ggplot(aes(x = pred, y = resid)) + geom_point(alpha = .3) +
  labs(title = "Residuals vs. Fitted Values")
```


#### Model Comparison

I'll compare my model to two others: 

* A model using length at birth and gestational age as predictors (Main Effects)
* One using head circumference, length, sex, and all interactions between these (Interaction Model)

```{r, warning=FALSE}
cv_df = crossv_mc(birthweight, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
    backwards_mod = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    mod_main_effect = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod_interaction = map(train, ~lm(bwt ~ bhead + blength + babysex 
                                     + bhead * blength 
                                     + bhead * babysex 
                                     + blength * babysex 
                                     + bhead * blength * babysex, data = .x)), 
    rmse_backwards_mod = map2_dbl(backwards_mod, test, ~rmse(model = .x, data = .y)),
    rmse_mod_main_effect = map2_dbl(mod_main_effect, test, ~rmse(model = .x, data = .y)),
    rmse_mod_interaction = map2_dbl(mod_interaction, test, ~rmse(model = .x, data = .y)))
  
```

Let's look at the results
```{r}
cv_df %>%
  select(starts_with("rmse")) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>%
  ggplot(aes(x = model, y = rmse)) + geom_violin() +
  labs(title = "RMSE for Cross-Validated Models", x = "Model Type", y = "RMSE")
```

The plot shows that the model made using the backward stepwise selection has the lowest RMSE, and therefore is the best performing of the three, in terms of predicting baby weight. The interaction model has a slightly greater RMSE than the proposed model, however the inclusion of interaction terms would make it harder to interpret than the other models. The main effect model had the largest RMSE.
